---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# flow

The goal of **flow** is to make it easy to extract numbers for population
defining flowcharts with minimal edits to existing **dplyr** workflows.

Note that this is an extremely early stage (practically idea concept) package.

## Installation

You can install the development version with:

``` r
# install.packages("devtools")
devtools::install_github("mikmart/flow")
```

## Example

You can `flow::track` the number of rows dropped with `dplyr::filter`:

```{r example-1, message = FALSE}
library(dplyr)

filtered <- mtcars %>%
  flow::track("1974 Motor Trend cars") %>%
  filter(mpg >= 20, mpg <= 30) %>%
  filter(cyl < 6)
```

The result looks like a regular tbl_df ...
```{r example-2}
filtered
```

... but the `filter` "history" can be extracted.
```{r example-3}
filtered %>% 
  flow::chart()
```
